Effect of character correlation

### 2022-03-24 Analysis/01-EffectCorrelationStats.Rmd
Updated results

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for each minimised (mini), maximised (maxi) and randomised (rand) character differences. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")

>>>>

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for each maximised, minimised and randomised correlation. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).")
